### 2023-09-20 main.tex
ert

@@

\paragraph{1. Useful relations}

@@

We first write and prove some relations that will be useful:

@@

By using \eqref{Dij-ref}, \eqref{Dii-ref} and observing that 

@@

We further observe that 

@@

\paragraph{3. Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 

@@

\paragraph{4. Final formula.} Using \eqref{Commutativity-Gained} and \eqref{k-times-QB} the symmetrization operator written in \eqref{W-charges-Bad} acting on the vacuum state $|\Psi_{0}^{0}\rangle$ reads, for all $k_{1},\ldots,k_{N-1}\in\mathbb{N}_{0}$

@@

Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have, for all $j\in{1,\ldots,k_{1}+\ldots+k_{N-1}}$ 
&\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\\=&

@@

Using the Euler $\Gamma$-function we have 

@@

>>>>

where $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for every $i\in\{1,\ldots,N-1\}$. 

@@

\paragraph{1. Useful relations} Here we derive some relations that are needed in the following of the proof. 

@@

We prove the following:

@@

Using \eqref{Dij-ref}, \eqref{Dii-ref} and observing that 

@@

As a further implication of \eqref{Two-Relation} we have

@@

\paragraph{3. Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, exploiting \eqref{Two-Relation} and \eqref{Commutativity-Gained} we obtain 

@@

\paragraph{4. Final formula.} For all $k_{1},\ldots,k_{N-1}\in\mathbb{N}_{0}$, using \eqref{Commutativity-Gained} and \eqref{k-times-LQB} the symmetrization operator introduced in \eqref{W-charges-Bad} acting on the vacuum state $|\Psi_{0}^{0}\rangle$ reads

@@

Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have, for all $j\in\{1,\ldots,k_{1}+\ldots+k_{N-1}\}$ 
&\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\nonumber\\=&

@@

introducing the Euler $\Gamma$-function we have 

@@

Observe that, while $S_{1}$ and $S_{2}$ are local, $W$ is not. 
